---
 title: "Pregunta 3 del capítulo 8."
---

#(Computer Experiment.)

Get the data on eruption times and waiting times between eruptions of the Old Faithful geyser from the website. Estimate the mean waiting time and give a standard error for the estimate. Also, give a 90 percent conﬁdence interval for the mean waiting time. Now estimate the median waiting time. In the next chapter we will see how to get the standard error for the median.


----------------------------------------------------------------------------------------
1) Estimador de la media.

````{r include = TRUE}
library(MASS)
hist(geyser$waiting,
     ylab = "Frecuencia",
     xlab = "Tiempo",
     main = "Tiempos de espera entre erupciones")
````
````{r include = TRUE}
table(geyser$waiting)
````
Como $n >30 $ usaremos los estimadores usuales.

````{r include = TRUE}
(media = mean(geyser$waiting))
(varhat = var(geyser$waiting))
````

Así el estimador de la media es 72.31438 y el de la varianza 192.9411.

----------------------------------------------------------------------------------------
2) Intervalo de confianza de la media.

Así construimos el intervalo de confianza al $95\%$.


````{r include = TRUE}
#Numero de observaciones
(n = dim(geyser)[1])
#alfa del nivel de confianza
alfa = 0.10
#intervalo al 95% de confianza
c(media + qnorm(alfa/2)*sqrt(varhat/n), media + qnorm(1-alfa/2)*sqrt(varhat/n))
````

----------------------------------------------------------------------------------------
3) Estimador de la mediana.

La mediana estimada es 76.


````{r include = TRUE}
datosOrdenados = geyser$waiting[order(geyser$waiting)]
if(n%%2 == 0){
  m = n/2
  mediana = mean(datosOrdenados[c(m,m+1)])
}else{
    m = (n-1)/2
  mediana = datosOrdenados[m+1]
}
````


